Network Data Model and BerlinMOD Benchmark

### 2010-03-26 Algebras/Network/BerlinMODNetwork/paper/PaperBerlinMODAndNetworkDataModel.tex
Actualised run times for BerlinMOD Network Experiments.

\subsection{Benchmark Results}
\label{sec:results}
We made several runs for each data amount and each query to get correct average execution times for each query in both data models. The tables \ref{tab:rtbmodb} and \ref{tab:rtnet} show the resulting run times for each query in seconds. Figure \ref{fig:compruntimesall} visualises the run time comparison between the different data models and approaches.
\begin{table}
\begin{scriptsize}
\begin{center}
\begin{tabular}{|c|r|r|r|r|r|r|}
\hline
&\multicolumn{2}{c|}{\textbf{Scalefactor 0.05}}&\multicolumn{2}{c|}{\textbf{Scalefactor 0.2}}&\multicolumn{2}{c|}{\textbf{Scalefactor 1.0}}\\
\hline
\textbf{Query}&\textbf{OBA}&\textbf{TBA}&\textbf{OBA}&\textbf{TBA}&\textbf{OBA}&\textbf{TBA}\\
\hline
\textbf{1}&0.09&0.12&0.11&0.11&x.xxx&x.xxx\\
\hline
\textbf{2}&$<$0.00&$<$0.00&$<$0.00&$<$0.00&x.xxx&x.xxx\\
\hline
\textbf{3}&0.33&0.32&0.42&0.48&x.xxx&x.xxx\\
\hline
\textbf{4}&8.94&14.00&32.54&71.83&x.xxx&x.xxx\\
\hline
\textbf{5}&1.19&1.58&1.65&2.86&x.xxx&x.xxx\\
\hline
\textbf{6}&15.19&13.09&63.91&105,53&x.xxx&x.xxx\\
\hline
\textbf{7}&3.09&3.09&14.20&10.51&x.xxx&x.xxx\\
\hline
\textbf{8}&0.35&0.39&0.40&0.42&x.xxx&x.xxx\\
\hline
\textbf{9}&88.68&183.96&212.80&468.76&x.xxx&x.xxx\\
\hline
\textbf{10}&143.06&37.54&660.18&146.34&x.xxx&x.xxx\\
\hline
\textbf{11}&0.17&0.12&0.22&0.18&x.xxx&x.xxx\\
\hline
\textbf{12}&0.29&0.13&4.06&0.20&x.xxx&x.xxx\\
\hline
\textbf{13}&10.07&7.10&27.11&13.18&x.xxx&x.xxx\\
\hline
\textbf{14}&0.49&0.53&1.10&1.16&x.xxx&x.xxx\\
\hline
\textbf{15}&1.02&0.77&7.78&3.65&x.xxx&x.xxx\\
\hline
\textbf{16}&43.44&12.40&28.54&24.08&x.xxx&x.xxx\\
\hline
\textbf{17}&1.09&0.95&8.20&4.40&x.xxx&x.xxx\\
\hline
\textbf{Total}&317.49&276.09&1063.13&853.69&x.xxx&x.xxx\\
\hline
\end{tabular}
\end{center}
\end{scriptsize}
\caption{Query Run Times \bmodb{}}
\label{tab:rtbmodb}
\end{table}
\begin{table}
\begin{scriptsize}
\begin{center}
\begin{tabular}{|c|r|r|r|r|r|r|}
\hline
&\multicolumn{2}{c|}{\textbf{Scalefactor 0.05}}&\multicolumn{2}{c|}{\textbf{Scalefactor 0.2}}&\multicolumn{2}{c|}{\textbf{Scalefactor 1.0}}\\
\hline
\textbf{Query}&\textbf{OBA}&\textbf{TBA}&\textbf{OBA}&\textbf{TBA}&\textbf{OBA}&\textbf{TBA}\\
\hline
\textbf{1}&0,19&0.10&0.17&0.10&x.xxx&x.xxx\\
\hline
\textbf{2}&$<$0.00&$<$0.00&$<$0.00&$<$0.00&x.xxx&x.xxx\\
\hline
\textbf{3}&0.38&0.55&0.56&0.85&x.xxx&x.xxx\\
\hline
\textbf{4}&0.36&1.46&0.56&7.65&x.xxx&x.xxx\\
\hline
\textbf{5}&1,19&1.58&2.51&2.27&x.xxx&x.xxx\\
\hline
\textbf{6}&5.13&4.12&20.59&14.67&x.xxx&x.xxx\\
\hline
\textbf{7}&9.54&7.04&32.58&37.27&x.xxx&x.xxx\\
\hline
\textbf{8}&0.20&0,22&0.29&0.29&x.xxx&x.xxx\\
\hline
\textbf{9}&21.73&23.23&38.09&49.06&x.xxx&x.xxx\\
\hline
\textbf{10}&85.70&82.13&419.98&317.15&x.xxx&x.xxx\\
\hline
\textbf{11}&0.42&0.92&2.08&2.93&x.xxx&x.xxx\\
\hline
\textbf{12}&0,21&0.23&0,23&0,25&x.xxx&x.xxx\\
\hline
\textbf{13}&1.11&1.36&5.31&5.49&x.xxx&x.xxx\\
\hline
\textbf{14}&3.03&3.75&8.53&8.99&x.xxx&x.xxx\\
\hline
\textbf{15}&0.63&0.52&2.89&2.17&x.xxx&x.xxx\\
\hline
\textbf{16}&0.58&1.46&0.32&0.70&x.xxx&x.xxx\\
\hline
\textbf{17}&0.22&0.32&0.28&0.99&x.xxx&x.xxx\\
\hline
\textbf{Total}&130.67&128.06&534.95&450.85&x.xxx&x.xxx\\
\hline
\end{tabular}
\end{center}
\end{scriptsize}
\caption{Query Run Times Network Data Model}
\label{tab:rtnet}
\end{table}
\begin{figure}
\begin{center}
	\includegraphics[width=17.0cm]{compruntimesall.eps}
	\caption{Compared Run Times for Each Query}
	\label{fig:compruntimesall}
\end{center}
\end{figure}

\section{New BerlinMOD Queries}
\label{sec:newqueries}
\section{Summary and Future Work}
\label{sec:summary}
Our experiments show that the network data model of moving in free space
 outperforms the \bmodb{} data model in the total query run time and in the most
single cases. The good results of the network data model encouraged us to extend
the \bmodb{} with a set of queries that enables us to compare the capabilities of
 different spatio-temporal network data models with respect to the specialized
 challenges of this data models.

>>>>

\subsection{Benchmark Results}
\label{sec:results}
We made several runs for each data amount and each query to get correct average execution times for each query in both data models. The tables \ref{tab:rtbmodb} and \ref{tab:rtnet} show the resulting run times for each query in seconds. Figure \ref{fig:compruntimesall} visualises the total run time comparison between the different data models and approaches for the three scalefactors. And figure \ref{fig:compqueryruntimes} compares the single query run times at scalefactor 1.0.
\begin{table}
\begin{scriptsize}
\begin{center}
\begin{tabular}{|c|r|r|r|r|r|r|}
\hline
&\multicolumn{2}{c|}{\textbf{Scalefactor 0.05}}&\multicolumn{2}{c|}{\textbf{Scalefactor 0.2}}&\multicolumn{2}{c|}{\textbf{Scalefactor 1.0}}\\
\hline
\textbf{Query}&\textbf{OBA}&\textbf{TBA}&\textbf{OBA}&\textbf{TBA}&\textbf{OBA}&\textbf{TBA}\\
\hline
\textbf{1}&0.086&0.100&0.146&0.123&0.226&0.166\\
\hline
\textbf{2}&0.003&0.00.&0.003&0.003&0.005&0.004\\
\hline
\textbf{3}&0.346&0.345&0.456&0.523&0.745&0.845\\
\hline
\textbf{4}&9.105&15.403&32.832&80.881&149.167&427.583\\
\hline
\textbf{5}&1.076&1.623&1.539&2.824&3.029&5.821\\
\hline
\textbf{6}&16.781&14.934&70.266&120.294&1463.214&5110.613\\
\hline
\textbf{7}&2.996&3.007&14.479&10.423&84.660&50.575\\
\hline
\textbf{8}&0.346&0.424&0.435&0.446&0.890&0.557\\
\hline
\textbf{9}&99.375&193.929&237.581&485.998&830.253&3153.720\\
\hline
\textbf{10}&139.795&36.636&605.718&139.565&4414.632&2015.096\\
\hline
\textbf{11}&0.143&0.111&0.233&0.149&0.656&0.914\\
\hline
\textbf{12}&0.297&0.133&4.332&0.160&36.210&0.213\\
\hline
\textbf{13}&11.284&7.341&1.30.173&13.791&119.685&94.366\\
\hline
\textbf{14}&0.525&0.727&1.115&1.166&10.912&3.915\\
\hline
\textbf{15}&1.201&0.802&8.824&4.286&30.874&18.711\\
\hline
\textbf{16}&43.567&5.346&29.389&5.500&35.490&8.655\\
\hline
\textbf{17}&1.084&0.935&8.453&4.169&82.242&343.826\\
\hline
\textbf{Total}&328.009&281.797&1045.974&870.300&7262.888&11235.581\\
\hline
\end{tabular}
\end{center}
\end{scriptsize}
\caption{Query Run Times \bmodb{}}
\label{tab:rtbmodb}
\end{table}
\begin{table}
\begin{scriptsize}
\begin{center}
\begin{tabular}{|c|r|r|r|r|r|r|}
\hline
&\multicolumn{2}{c|}{\textbf{Scalefactor 0.05}}&\multicolumn{2}{c|}{\textbf{Scalefactor 0.2}}&\multicolumn{2}{c|}{\textbf{Scalefactor 1.0}}\\
\hline
\textbf{Query}&\textbf{OBA}&\textbf{TBA}&\textbf{OBA}&\textbf{TBA}&\textbf{OBA}&\textbf{TBA}\\
\hline
\textbf{1}&0.090&0.113&0.082&0.092&0.185&0.215\\
\hline
\textbf{2}&0.003&0.002&0.004&0.003&0.019&0.004\\
\hline
\textbf{3}&0.112&0.568&0.134&0.834&0.845&1.323\\
\hline
\textbf{4}&0.142&1.303&0.217&7.504&1.145&31.879\\
\hline
\textbf{5}&0.927&1.377&1.768&2.251&4.781&5.277\\
\hline
\textbf{6}&5.004&4.483&20.605&14.884&381.622&263.371\\
\hline
\textbf{7}&1.221&6.790&10.107&35.036&124.602&169.848\\
\hline
\textbf{8}&0.225&0.213&0.202&0.225&0.258&0.303\\
\hline
\textbf{9}&22.935&24.349&41.579&50.853&120.470&156.693\\
\hline
\textbf{10}&81.770&84.298&378.248&309.345&2786.578&1791.941\\
\hline
\textbf{11}&0.158&0.898&0.178&3.017&6.030&7.738\\
\hline
\textbf{12}&0.228&0.202&0.269&0.260&0.274&0.267\\
\hline
\textbf{13}&1.159&1.336&5.737&5.248&29.126&36.086\\
\hline
\textbf{14}&0.793&3.734&1.469&9.286&36.041&38.552\\
\hline
\textbf{15}&0.625&0.543&2.644&2.084&10.317&7.989\\
\hline
\textbf{16}&0.680&1.579&0.376&0.847&0.584&1.969\\
\hline
\textbf{17}&0.234&0.337&0.306&0.923&0.550&8.026\\
\hline
\textbf{Total}&116.305&132.127&463,926&442.691&3503.429&2521.481\\
\hline
\end{tabular}
\end{center}
\end{scriptsize}
\caption{Query Run Times Network Data Model}
\label{tab:rtnet}
\end{table}
\begin{figure}
\begin{center}
	\includegraphics[width=17.0cm]{compruntimesall.eps}
	\caption{Compared Total Query Run Times for each Scalefactor}
	\label{fig:compruntimesall}
\end{center}
\end{figure}
\begin{figure}
\begin{center}
   \includegraphics[width=17.0cm]{compqueryruntimes.eps}
   \caption{Compared Run Times for Each Query at Scalefactor 1.0}
   \label{fig:compqueryruntimesall}
\end{center}
\end{figure}
\section{New BerlinMOD Queries}
\label{sec:newqueries}
\section{Summary and Future Work}
\label{sec:summary}
Our experiments show that the network data model of moving in free space
 outperforms the \bmodb{} data model in the total query run time and in the most
single cases. The good results of the network data model encouraged us to extend
the \bmodb{} with a set of queries that enables us to compare the capabilities of
 different spatio-temporal network data models with respect to the specialized
 challenges of this data models.
